Importance of depth refugia for reef resilience and intervention on the Great Barrier Reef under future climate change

### 2025-10-10 paper/paper_draft.qmd
Tweak intro

Climate change is impacting species survival, persistence and ecosystem functions on coral
reefs, which are vulnerable to increasing magnitude and variation in environmental stressors
such as ocean temperature [@foster2021; @gattuso2014]. Mass bleaching and associated
mortality events driven by climate change can cause reef-building coral population declines
[@hughes2017; @hughes2018; @bozec2025], possibly leading to coral-macroalgae regime shifts
[@arif2022; @wild2011]. Climate impacts on coral reefs are decreasing the ability of coral
reefs to provide ecological functions such as benthic habitat and nutrient cycling
[@forster2021; @williams2019] and services such as food, protection, tourism and Indigenous
cultural value [@eddy2021; @stoeckl2021].

Coral reef ecosystem resilience - the capacity to maintain coral populations and avoid
ecosystem regime shifts - is conceptualised to depend on three interconnected mechanisms.
First, the ability of individual corals to survive thermal stress. Second, the connectivity
networks that enable recolonisation after disturbances [@hock2017; @mumby2008; @torres2024].
Third, the maintenance, and accretion, of the carbonate framework that provides reef
structure [@perry2012]. This investigation aims to assess how these mechanisms interact
under projected climate conditions to identify the characteristics of resilient reefs in the
Great Barrier Reef (GBR) ecosystem.

>>>>

Climate change is impacting species survival, persistence and ecosystem functions on coral
reefs, which are vulnerable to increasing magnitude and variation in environmental stressors
such as ocean temperature [@foster2021; @gattuso2014]. Mass bleaching and associated
mortality events driven by climate change can cause coral population declines [@hughes2017;
@hughes2018; @bozec2025], possibly leading to coral-macroalgae regime shifts [@arif2022;
@wild2011]. Climate impacts on coral reefs are decreasing the ability of coral reefs to
provide ecological functions such as benthic habitat and nutrient cycling [@forster2021;
@williams2019] and services such as food, protection, tourism and Indigenous cultural value
[@eddy2021; @stoeckl2021].

Here, coral reef ecosystem resilience - the capacity to maintain coral populations and avoid
ecosystem regime shifts - is conceptualised to depend on three interconnected mechanisms.
First, the ability of individual corals to survive thermal stress. Second, the connectivity
networks that enable recolonisation after disturbances [@hock2017; @mumby2008; @torres2024].
Third, the maintenance, and accretion, of the carbonate framework that provides reef
structure [@perry2012]. This investigation aims to assess how these mechanisms may interact
under projected climate conditions to identify the characteristics of resilient reefs in the
Great Barrier Reef (GBR) ecosystem.
